---
name: Max Czapanskiy, PhD
position: "UC Santa Barbara, Assistant Professor of Teaching"
profilepic: headshot.jpg
email: "maxczapanskiy@gmail.com"
github: FlukeAndFeather
www: flukeandfeather.com
orcid: 0000-0002-6302-905X
headcolor: 619D8C
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), sprintf("Czapanskiy_CV_%s", Sys.Date()))) })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)
source("util.R")
```

Ecologist, data scientist, and educator. I teach scientists at all career stages how to improve their data analysis skills through innovative course design and hands-on mentorship. My research integrates software engineering and ecology to promote open and reproducible science.

# Education

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "PhD in Biology", "Stanford University", "Pacific Grove, CA", "2022",
  list("Advised by Jeremy Goldbogen",
       "Dissertation: Baleen whale physiology revealed through the integration of bio-logging and ecoinformatics"),
  "MS in Geographic Information Systems", "San Francisco State University", "San Francisco, CA", "2018",
  list("Advised by Ellen Hines",
       "Thesis: Using energy landscapes to understand seabird movement and spatial ecology",
       "Graduate hood, College of Science \\& Engineering"),
  "BS in Computer Science", "Columbia University", "New York, NY", "2014", 
    list()) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```

# Teaching and Mentoring

```{r teaching}
tribble(
  ~ year, ~ title, ~ institution, ~ role, ~ details,
  "2023",
    "Data Science for Eco/Evo",
    "UC Santa Cruz",
    "Lead instructor",
    list(
      "Graduate seminar in the Department of Eco and Evo Bio covering scientific programming, project management, and open science.",
      "Course website: flukeandfeather.github.io/BIOE215fall23/"
    ),
  "2022",
    "Undergraduate researcher mentor",
    "Stanford University",
    "REEFS Mentor",
    list(),
  "2021", 
    "Just Enough Software Engineering (For Scientists)",
    "Stanford University",
    "Lead instructor",
    list(
      "Two-week self-directed, mastery-oriented software engineering course for biosciences graduate students"
    ),
  "2021",
    "Introduction to Physiological Ecology",
    "Stanford University",
    "Teaching assistant",
    list(),
  "2019",
    "Undergraduate researcher mentor",
    "CSU Monterey Bay REU",
    "NSF REU Mentor",
    list(
      "Mentee Hayden Smith presented his work at a conference and published it in the \\textit{Journal of Exp. Bio.} (Gough et al., 2021)."
    ),
  "2018 - present",
    "Data Carpentry",
    "The Carpentries",
    "Certified Instructor",
    list(),
  "2018",
    "Introduction to Ecology",
    "Stanford University",
    "Teaching assistant",
    list(),
  "2016 - 2017",
    "Introduction to GIS",
    "San Francisco State University",
    "Teaching assistant",
    list()
) %>% 
  detailed_entries(
    with = title,
    what = role,
    when = year,
    where = institution,
    why = details,
    .protect = FALSE
  )
```

# Publications

```{r publications}
bib2df::bib2df("works.bib") %>% 
  mutate(AUTHOR = map_chr(AUTHOR, combine_authors)) %>% 
  detailed_entries(
    what = AUTHOR,
    when = YEAR, 
    with = TITLE, 
    where = JOURNAL,
    .protect = FALSE
  )
```

## Technical reports

```{r reports}
tribble(
  ~ year, ~ title, ~ authors, ~ report,
  2020,
    "Habitat Affinities and At-Sea Ranging Behaviors among Main Hawaiian Island Seabirds: Breeding Seabird Telemetry, 2013–2016.",
    "Adams, J., Felis, J.J., \\textbf{Czapanskiy, M.F.}",
    "OCS Study BOEM 2020-006.",
  2019,
    "Trends in mammalian predator control trapping events intended to protect ground-nesting, endangered birds at Haleakalā National Park, Hawaiʻi: 2000–14.",
    "Kelsey, E.C., Adams, J., \\textbf{Czapanskiy, M.F.}, Felis, J.J., Yee, J.L., Kaholoaa R.L., and Bailey, C.N.",
    "U.S. Geological Survey Open-File Report 2019–1122."
) %>% 
  detailed_entries(
    what = authors,
    with = title,
    where = report,
    when = year,
    .protect = FALSE
  )
```

# Software

```{r software}
tribble(
  ~ software, ~ link, ~ language, ~ details,
  "stickleback", "(pypi.org/project/stickleback)", "Python",
    "A machine learning pipeline for detecting fine-scale behavioral events in bio-logging data",
  "rstickleback", "(github.com/FlukeAndFeather/rstickleback)", "R",
    "An R interface to the stickleback machine learning pipeline",
  "catsr", "(doi.org/10.5281/zenodo.5140484)", "R",
    "Tools for reading and visualizing 3D bio-logging data; accompanies Cade et al. (2021)",
  "beats", "(github.com/FlukeAndFeather/beats)", "R",
    "Interactive tools for importing, annotating, and validating ECG bio-logger data"
) %>% 
  mutate(software = sprintf("%s %s", software, link)) %>% 
  detailed_entries(
    what = details,
    when = language,
    with = software,
    .protect = FALSE
  )
```

# Employment

```{r work}
tribble(
  ~ what, ~ when, ~ with,
  "Assistant Professor of Teaching",
    "2024 - Present",
    "UC Santa Barbara, Bren School & College of Creative Studies",
  "Postdoctoral Scholar",
    "2022 - 2024",
    "NOAA / UC Santa Cruz",
  "Stanford Data Science Scholar",
    "2019 - 2021",
    "Stanford University",
  "Biological Sciences Technician",
    "2014 - 2017",
    "U.S. Geological Survey Western Ecological Research Center",
  "Avian Point Count Technician",
    "2014",
    "University of Montana Avian Science Center",
  "Field Assistant and Data Analyst",
    "2012 - 2013",
    "Friends of Cooper Island",
  "Marine Ecology Intern",
    "2013",
    "Point Blue Conservation Science",
  "Software Developer Engineer in Test",
    "2009 - 2012",
    "Microsoft"
) %>% 
  detailed_entries(what, when, with)
```

# Conference presentations

```{r conferences}
tribble(
  ~ year, ~ title, ~ conference, ~ location,
  "2021",
    "Stickleback: A machine learning pipeline for detecting behavioral events in bio-logging data",
    "7th International Bio-Logging Symposium",
    "Online",
  "2018",
    "Quantifying the Influence of Energy Windscapes on Seabird Distributions",
    "Ocean Sciences Meeting",
    "Portland, OR",
  "2017",
    "Modeling Seabird Habitat Accessibility",
    "Society for Conservation GIS Annual Conference",
    "Pacific Grove, CA",
  "2016",
    "Taking the Plunge: Comparing Diving Behavior of Red-footed and Brown Boobies Breeding on Lehua Islet, Hawaii",
    "Pacific Seabird Group Annual Meeting",
    "Turtle Bay, HI"
) %>% 
  detailed_entries(
    what = conference,
    with = title,
    when = year,
    where = location,
    .protect = FALSE
  )
```

# Awards and scholarships

```{r awards}
tribble(
  ~ year, ~ title, ~ from, ~ where,
  "2020",
    "Stanford Data Science Scholar Fellowship",
    "Stanford Data Science Initiative",
    "Stanford University",
  "2019",
    "Outstanding Teaching Assistant Award",
    "Department of Biology",
    "Stanford University",
  "2018",
    "Stanford Graduate Fellowship",
    "Vice Provost for Graduate Education",
    "Stanford University",
  "2018",
    "Graduate Hood",
    "College of Science and Engineering",
    "San Francisco State University",
  "2018",
    "Student of the Year",
    "Esri Development Center",
    "Esri",
  "2018",
    "COAST Reasearch Award",
    "Council on Ocean Affairs",
    "California State University",
  "2017",
    "Maxwell Memorial Scholarship",
    "College of Science and Engineering",
    "San Francisco State University",
  "2017",
    "Pease Award",
    "Department of Geography and Environmentt",
    "San Francisco State University",
  "2017",
    "CWEP Award for Graduate Student Writing",
    "University Committee on Written English Proficiency",
    "San Francisco State University"
) %>% 
  detailed_entries(
    what = title,
    with = from,
    when = year,
    where = where,
    .protect = FALSE
  )
```
