---
name: Max Czapanskiy, PhD
position: "Ecology | Data Science"
email: "maxczapanskiy@gmail.com"
github: FlukeAndFeather
www: flukeandfeather.com
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), sprintf("Czapanskiy_CV_%s", Sys.Date()))) })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)
source("util.R")
```

# Education

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "PhD in Biology", "Stanford University", "Pacific Grove, CA", "2022",
  list("Advised by Jeremy Goldbogen",
       "Dissertation: Baleen whale physiology revealed through the integration of bio-logging and ecoinformatics"),
  "MS in Geographic Information Systems", "San Francisco State University", "San Francisco, CA", "2018",
  list("Advised by Ellen Hines",
       "Thesis: Using energy landscapes to understand seabird movement and spatial ecology",
       "Graduate hood, College of Science \\& Engineering"),
  "BS in Computer Science", "Columbia University", "New York, NY", "2014", 
    list()) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```

# Employment

```{r work}
tribble(
  ~ what, ~ when, ~ with,
  "Postdoctoral Scholar",
    "2022 - present",
    "NOAA / UC Santa Cruz",
  "Stanford Data Science Scholar",
    "2019 - 2021",
    "Stanford University",
  "Biological Sciences Technician",
    "2014 - 2017",
    "U.S. Geological Survey Western Ecological Research Center",
  "Avian Point Count Technician",
    "2014",
    "University of Montana Avian Science Center",
  "Field Assistant and Data Analyst",
    "2012 - 2013",
    "Friends of Cooper Island",
  "Marine Ecology Intern",
    "2013",
    "Point Blue Conservation Science",
  "Software Developer Engineer in Test",
    "2009 - 2012",
    "Microsoft"
) %>% 
  detailed_entries(what, when, with)
```

# Publications

```{r publications}
bib2df::bib2df("works.bib") %>% 
  mutate(AUTHOR = map_chr(AUTHOR, combine_authors)) %>% 
  detailed_entries(
    what = AUTHOR,
    when = YEAR, 
    with = TITLE, 
    where = JOURNAL,
    .protect = FALSE
  )
```

## In review
```{r in-review}
bib2df::bib2df("review.bib") %>% 
  mutate(AUTHOR = map_chr(AUTHOR, combine_authors)) %>% 
  detailed_entries(
    what = AUTHOR,
    with = TITLE, 
    where = JOURNAL,
    .protect = FALSE
  )
```

## Technical reports

```{r reports}
tribble(
  ~ year, ~ title, ~ authors, ~ report,
  2020,
    "Habitat Affinities and At-Sea Ranging Behaviors among Main Hawaiian Island Seabirds: Breeding Seabird Telemetry, 2013–2016.",
    "Adams, J., Felis, J.J., \\textbf{Czapanskiy, M.F.}",
    "OCS Study BOEM 2020-006.",
  2019,
    "Trends in mammalian predator control trapping events intended to protect ground-nesting, endangered birds at Haleakalā National Park, Hawaiʻi: 2000–14.",
    "Kelsey, E.C., Adams, J., \\textbf{Czapanskiy, M.F.}, Felis, J.J., Yee, J.L., Kaholoaa R.L., and Bailey, C.N.",
    "U.S. Geological Survey Open-File Report 2019–1122."
) %>% 
  detailed_entries(
    what = authors,
    with = title,
    where = report,
    when = year,
    .protect = FALSE
  )
```

# Teaching and Mentoring

```{r teaching}
tribble(
  ~ year, ~ title, ~ institution, ~ role, ~ details,
  "2022",
    "Undergraduate researcher mentor",
    "Stanford University",
    "REEFS Mentor",
    list(
      "Mentored Lilah McCormick in quantitative ecophysiology.",
      "Lilah learned reproducible research techniques in R and is writing a paper about measuring cardiac function in narwhals."
    ),
  "2021", 
    "Just Enough Software Engineering (For Scientists)",
    "Stanford University",
    "Lead instructor and course designer",
    list(
      "Self-directed, mastery-oriented software engineering course for biosciences graduate students",
      "Two-week intensive short course"
    ),
  "2021",
    "Introduction to Physiological Ecology",
    "Stanford University",
    "Teaching assistant",
    list(),
  "2019",
    "Undergraduate researcher mentor",
    "CSU Monterey Bay REU",
    "NSF REU Mentor",
    list(
      "Mentored Hayden Smith in quantitative analysis.",
      "Hayden presented his work at the 2020 Society for Int. and Comp. Bio. Meeting and published it in the \\textit{Journal of Exp. Bio.} (Gough et al., 2021)."
    ),
  "2018 - present",
    "Data Carpentry",
    "The Carpentries",
    "Certified Instructor",
    list(),
  "2018",
    "Introduction to Ecology",
    "Stanford University",
    "Teaching assitant",
    list(),
  "2016 - 2017",
    "Introduction to GIS",
    "San Francisco State University",
    "Teaching assistant",
    list()
) %>% 
  detailed_entries(
    with = title,
    what = role,
    when = year,
    where = institution,
    why = details,
    .protect = FALSE
  )
```

# Software

```{r software}
tribble(
  ~ software, ~ link, ~ language, ~ details,
  "stickleback", "(pypi.org/project/stickleback)", "Python",
    "A machine learning pipeline for detecting fine-scale behavioral events in bio-logging data",
  "rstickleback", "(github.com/FlukeAndFeather/rstickleback)", "R",
    "An R interface to the stickleback machine learning pipeline",
  "catsr", "(doi.org/10.5281/zenodo.5140484)", "R",
    "Tools for reading and visualizing 3D bio-logging data; accompanies Cade et al. (2021)",
  "beats", "(github.com/FlukeAndFeather/beats)", "R",
    "Interactive tools for importing, annotating, and validating ECG bio-logger data"
) %>% 
  mutate(software = sprintf("%s %s", software, link)) %>% 
  detailed_entries(
    what = details,
    when = language,
    with = software,
    .protect = FALSE
  )
```

# Conference presentations

```{r conferences}
tribble(
  ~ year, ~ title, ~ conference, ~ location,
  "2021",
    "Stickleback: A machine learning pipeline for detecting behavioral events in bio-logging data",
    "7th International Bio-Logging Symposium",
    "Online",
  "2018",
    "Quantifying the Influence of Energy Windscapes on Seabird Distributions",
    "Ocean Sciences Meeting",
    "Portland, OR",
  "2017",
    "Modeling Seabird Habitat Accessibility",
    "Society for Conservation GIS Annual Conference",
    "Pacific Grove, CA",
  "2016",
    "Taking the Plunge: Comparing Diving Behavior of Red-footed and Brown Boobies Breeding on Lehua Islet, Hawaii",
    "Pacific Seabird Group Annual Meeting",
    "Turtle Bay, HI"
) %>% 
  detailed_entries(
    what = conference,
    with = title,
    when = year,
    where = location,
    .protect = FALSE
  )
```

# Awards and scholarships

* Stanford Data Science Scholar Fellowship, Stanford Data Science Initiative (2020)
* Stanford Graduate Fellowship, Vice Provost for Graduate Education (2018)
* Graduate Hood, San Francisco State University, College of Science and Engineering (2018)
* Esri Development Center Student of the Year, Esri (2018)
* COAST Research Award, California State University, Council on Ocean Affairs (2018)
* Maxwell Memorial Scholarship, San Francisco State University, College of Science and Engineering (2017)
* Pease Award, San Francisco State University, Department of Geography and Environment (2017)
* CWEP Award for Graduate Student Writing, San Francisco State University (2017)
